Initial Analysis

### 2019-05-23 Initial_Analysis.Rmd
Changed proportion to b species bazed

### Notes
# Function originally created by William (#WC)
# Juliano modifications (#JC)
# This funtion is used in estAbdBinTemp.R
# We are using only summer distribution

### Variables used
# spplisttemp <- Species list template. Information of the species used in the DBEM under TaxaDataC. 
# Distpath <- Path to where the initial distribution of the species is. AKA. Files that start with "S"

#### The function

@@

  # Get model data from spps
  SppDist <- GetSppDist(600004,"All")

  Index_EEZ <- Neighbors %>% 
    select(INDEX)
      # Result 1. Number of Countries that share the species
  # Trans_Index

  Trans_Spp <- suppressWarnings(SppDist %>%
    gather("Model","Value",3:6) %>%
    filter(
      INDEX %in% Index_EEZ$INDEX,
      Value != 0
      ) %>%
    left_join(Neighbors,
              by = "INDEX") %>% # Match the species distribution to the Countries EEZs
    group_by(Name = Country_Territory,
             Neighbor_Territory,
             TaxonKey,
             Model
             ) %>% 
    summarise(n_cells_spp = n()) %>% # The number of cells present within each country's EEZ
    left_join(EEZ_Size,
              by = "Name") %>% 
    mutate(Trans_Index = n_cells_spp/n_tot_grid) %>%  # Include one transboundary species
    select(EEZID,everything())
    ) # For the sake of my brain

@@

### Testing Function ####
# Spp <- 600006
# Model <- "All"
# EEZ_Size <- EEZ_Size
# Neighbors <- Neighbor_List

@@

Test_Countries <-c("Guatemala (Caribbean)","Guatemala (Pacific)","Belize","Honduras","El Salvador","Costa Rica (Pacific)","Costa Rica (Caribbean)", "Panama (Caribbean)", "Panama (Pacific)")

>>>>

#### The function
# NOTES
# For now we're using only the last 10 years average, basicaaly if the species has been fished in any of these years, its considered present

@@

  # Get model data from spps
  SppDist <- GetSppDist(Spp,Model)
  # suppressWarnings(

  # Estimate total spp distribution within neighbours
  Spp_Total_Dist <- SppDist %>%
    gather("Model","Value",3:6) %>%
    filter(
      INDEX %in% Index_EEZ$INDEX,
      Value != 0
    ) %>% 
    # group_by(INDEX) %>% 
    # summarise(n()) %>% 
    left_join(Neighbors,
              by = "INDEX") %>% 
    group_by(Name = Country_Territory,
             Neighbor_Territory,
             Model) %>% 
    summarise(n_cells_spp = n()) %>% 
    ungroup()

  # Split dataframes to merge latter
  Tone <- select(Spp_Total_Dist,1,3,4)
  Ttwo <- select(Spp_Total_Dist,Name=2,3,4) # Change column name

  # Merge dataframes
  Merged_data <- merge(Tone,Ttwo, by = c("Name","Model")) %>% 
    rowwise() %>% 
    mutate(Total = sum(n_cells_spp.x,n_cells_spp.y)) %>% 
    select(Name,Model,Total) %>% 
    left_join(Spp_Total_Dist,
              by = c("Name","Model")) %>% 
    select(Name,Model,Total)

  # Get the index for testing
  Index_EEZ <- Neighbors %>% 
    select(INDEX)

  # Result 1. Number of Countries that share the species
  # Trans_Index

  Trans_Spp <- suppressWarnings(SppDist %>%
    gather("Model","Value",3:6) %>%
    filter(
      INDEX %in% Index_EEZ$INDEX,
      Value != 0
      ) %>%
    left_join(Neighbors,
              by = "INDEX") %>% # Match the species distribution to the Countries EEZs
    group_by(Name = Country_Territory,
             Neighbor_Territory,
             TaxonKey,
             Model
             ) %>% 
    summarise(n_cells_spp = n()) %>% # The number of cells present within each country's EEZ
    # Commented out because EEZ size might not be the best
      # left_join(EEZ_Size,
    #           by = "Name") %>% 
      # Trying with the distribution of the speices
      left_join(Merged_data,
              by = c("Name","Model")) %>% 
    mutate(Trans_Index = n_cells_spp/Total) %>%  # Include one transboundary species
    group_by(Name,Neighbor_Territory,TaxonKey) %>% 
      summarise(Mean_Trans = mean(Trans_Index))
    )# Mean of all data

@@

### Testing Function ####
Spp <- 600006
Model <- "All"
EEZ_Size <- EEZ_Size
Neighbors <- Neighbor_List

@@

Test_Countries <-c("Guatemala (Caribbean)","Guatemala (Pacific)","Belize","Honduras (Pacific)","El Salvador","Costa Rica (Pacific)","Costa Rica (Caribbean)", "Panama (Caribbean)", "Panama (Pacific)")
